% First parameter can be changed eg to "Glossary" or something.
% Second parameter is the max length of bold terms.
\begin{mclistof}{List of publications}{0cm}
	%\item[] All quantities are defined in SI units unless otherwise specified throughout the thesis.
	%\item[$\alpha$] Twiss parameter = $-\frac{\langle x_i x'_i \rangle}{\epsilon^i_\mathrm{rms}}$
	\begin{enumerate}
		\item \textbf{R.J.L. Timmis}, A. James, H. Martin, J. Lee, M.W. von der Leyen, E. Gumbrell, and P.A. Norreys. X-ray HHG on the ORION petawatt laser facility. \textit{Reports on Progress in Phyiscs}, preparing for submission.
		\item \textbf{R.J.L. Timmis}, R.W. Paddock, I. Ouatu, J. Lee, S. Howard, E. Atonga, R.T. Ruskov, H. Martin, R.H.W. Wang, R. Aboushelbaya, M.W. von der Leyen, E. Gumbrell, and P.A. Norreys. Attosecond and nano-Coulomb electron bunches via the Zero Vector Potential mechanism. \textit{Scientific Reports}, post-peer review.
		% Go here to get preprint link once it is created: https://www.researchsquare.com/article/rs-4248053/private/timeline
		\item H. Martin, R. Paddock, M. von der Leyen, V. Eliseev, R.T. Ruskov, \textbf{R. Timmis}, J. Lee, A. James, and P.A. Norreys. Electrothermal Filamentation of Fusion Plasmas. \textit{Physical Review Letters}, under consideration. 
		\item M.W. von der Leyen, J. Holloway, Y. Ma, P.T. Campbell, R. Aboushelbaya, Q. Qian, A.F. Antoine, M. Balcazar, J. Cardarelli, Q. Feng, R. Fitzgarrald, B.X. Hou, G. Kalinchenko, J. Latham, A.M. Maksimchuk, A. McKelvey, J. Nees, I. Ouatu, R.W. Paddock, B. Spiers, A.G.R. Thomas, \textbf{R. Timmis}, K. Krushelnick, and P.A. Norreys. Observation of Monoenergetic Electrons from Two-Pulse Ionization Injection in Quasilinear Laser Wakefields. \textit{Physical Review Letters} \textbf{130}, 105002 (2023).
		\item J.J. Lee, R.T. Ruskov, H. Martin, S. Hughes, M.W. von der Layen, R.W. Paddock, \textbf{R. Timmis}, I. Ouatu, Q.S. Feng, S. Howard et al. Toward more robust ignition of inertial fusion targets. \textit{Physics of Plasmas} \textbf{30}, 022702 (2023).
		\item R.W. Paddock, H. Martin, R.T. Ruskov, R.H.H. Scott, W. Garbett, B.M. Haines, A.B. Zylstra, E.M. Campbell, T.J.B. Collins, R.S. Craxton C.A. Thomas, V.N. Goncharov, R. Aboushelbaya, Q.S. Feng, M.W. von der Leyen, I. Ouatu, B.T. Spiers, R. Timmis, R.H.W. Wang and, P.A. Norreys. Pathways towards break even for low convergence ratio direct-drive inertial confinement fusion. \textit{Journal of Plasma Physics} \textbf{88} 3 (2022).
		\item I. Ouatu, B.T. Spiers, R. Aboushelbaya, Q. Feng, M.W. von der Leyen, R.W. Paddock, \textbf{R. Timmis}, C. Ticos, K.M. Krushelnick, and P.A. Norreys. Ionization states for the multipetawatt laser-QED regime. \textit{Physics Review E} \textbf{106}, 015205 (2022).
		\item Q.S. Feng, R. Aboushelbaya, M.W. von der Leyen, B.T. Spiers, R.W. Paddock, I. Ouatu, R. Timmis, R.H.W. Wang, L.H. Cao, Z.J. Liu, C.Y. Zheng, X.T. He, and P.A. Norreys. Suprathermal electrons from the anti-Stokes Langmuir decay instability cascade. \textit{Physical Review E} \textbf{105}, 045208 (2022).
		\item B.T. Spiers, R. Aboushelbaya, Q. Feng, M.W. Mayr, I. Ouatu, R.W. Paddock, \textbf{R. Timmis}, R.H.W. Wang, and P.A. Norreys. Methods for extremely sparse-angle proton tomography. \textit{Physical Review E} \textbf{104}, 045201 (2021).
		% TODO add eduards paper
	\end{enumerate}
	
\end{mclistof} 
